Insert your title here

### 2019-06-14 prod/paper/paper_draft.tex
first draft of paper

\title{Insert your title here%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{Do you have a subtitle?\\ If so, write it here}

\titlerunning{Short form of title}        % if too long for running head

@@

\authorrunning{Short form of author list} % if too long for running head

%\institute{F. Author \at
%              first address \\
%              Tel.: +123-45-678910\\
%              Fax: +123-45-678910\\
%              \email{bfarzin@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
%           \and
%           S. Author \at
%              second address
%}

@@

\begin{abstract}

All the code for this project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference.  Some details are omitted below for clarity but can be found in the notebooks, code and execution instructions.

@@

\section{Introduction}
\label{intro}

\paragraph{Contribution} Our contribution with this work is..

@@

\begin{figure}[h]
	% Use the relevant command to insert your figure file.
	% For example, with the graphicx package use
	\includegraphics[width=0.75\textwidth]{seed_hist_f1}
	\caption{Histogram of F1 metric averaged across 5-fold metric}
	\label{fig:random_seed_hist}
\end{figure}

\section{Conclusion}
\label{sec:5}

>>>>

\title{Insert your title here%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

@@

%\authorrunning{Short form of author list} % if too long for running head
\institute{}
%\institute{F. Author \at
%              first address \\
%              Tel.: +123-45-678910\\
%              Fax: +123-45-678910\\
%              \email{bfarzin@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
%           \and
%           S. Author \at
%              second address
%}

@@

\begin{abstract}
Our entry into the \textit{HAHA 2019 Challenge} came in $3^{rd}$ in the classification task and $2^{nd}$ in the regression task.  We describe our system and innovations and compare our results to a Naive Bayes classifier.  All the code for ourproject is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and replication by others.

@@

\section{Introduction}
\label{intro}
\newcommand{\chapquote}[3]{\begin{quotation} \textit{#1} \end{quotation} \begin{flushright} - #2, \textit{#3}\end{flushright} }

\begin{quote}
- !`Socorro, me ha picado una víbora!\\
- ?`Cobra?\\
- No, gratis.\footnote{https://www.fluentin3months.com/spanish-jokes/}
\end{quote}
Google Translation:
\begin{quote}
- Help, I was bitten by a snake!\\
- Does it charge?\\
- Not free.
\end{quote}
Humor does not translate well because it often relies on double-meaning or a subtle play on the words or context.  Thus, one would imagine building a system to classify the humor of tweets would be difficult.  However, with transfer-learning and the Fastai libray\footnote{https://docs.fast.ai/}, you can quickly get a high quality classifier working in a language you don't even speak which will easily out-pace a Naive Bayes SVM baseline \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}

Rather than hand-crafted language features, we have taken an "end to end" approach building from the raw text to a final model that achieve the tasks as presented.  Our paper lays out the details of the system and our code can be found in a GitHub repo for use by other researchers to extend the state of the art in sentiment analysis.

\paragraph{Contribution} Our key contributions are three fold.  First, we apply transfer-learning of a lanugage model based on a larger corpus of tweets.  Second, we use a label smoothed loss to allow full training of the final model without gradual unfreezing.  Third, we select the best classifier or regression model based on cross-validation and 20 random-seed initialization in the final network training step.

@@

\begin{figure}[ht]
	% Use the relevant command to insert your figure file.
	% For example, with the graphicx package use
	\includegraphics[width=0.75\textwidth]{seed_hist_f1}
	\caption{Histogram of F1 metric averaged across 5-fold metric}
	\label{fig:random_seed_hist}
\end{figure}

\subsection{Results}
Below in Table \ref{tab:tab_results} we layout three results from our submissions in the competition.  The first is the Naive Bays SVM solution showing an F1 of 0.7548.  Second is our first random seed selected for the classifier which produces a 0.8083 result.  While better than the NBSVM solution, we can do better by picking the best F1 from the 20 seeds that we selected. That result is in the final row and gets our final submission value of 0.8099. Note that in our validation set achieved an F1 of 0.8254 but this is somewhat overfit from the many trials we have run and our final test set is a drop of 0.0155

\begin{table}[ht]
	% table caption is above the table
	\caption{Comparative Results}
	\label{tab:tab_results}
	\begin{tabular}{lllll}
		\hline\noalign{\smallskip}
		 & Accuracy & Precision & Recall & F1 \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
NBSVM &      0.8223 & 0.8180 & 0.7007 & 0.7548 \\
First Seed & 0.8461 & 0.7869 & 0.8309 & 0.8083 \\
Best Seed &  0.8458 & 0.7806 & 0.8416 & \textbf{0.8099} \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}

\section{Conclusion}
\label{sec:5}
This paper describes our implementation of a neural net model for classification and regression in the HAHA 2019 challenge.  Our solution placed third in Task 1 and second in task 2 in the final standings.  We describe the data collection, pre-training and final model building steps.  Additionally, we have open-sourced all the code used in this contest so it can be easily duplicate to further research in this task in the future.
